UKB Models

### 2023-11-03 ukb_curation-eda.Rmd
save out age-filt df to csv for permuting sites on with qsub

```{r}
cn_data <- fread(file="data/lifespan_dataset_dkatlas_CNonly.csv")
#table(cn_data$study)
```

@@

```{r}
ukb_df_age.filt <- ukb_df_totals %>%
  dplyr::filter(age_yrs >= 50 & age_yrs <= 80)
# #write data
# write_csv(ukb_df_age.filt, file="data/ukb_CN_data_agefilt.csv")
```

@@

@@

# View the final dataframe
print(ukb_df_sites_perm)
#names(ukb_df_sites_perm)
```
```{r}
sim.perm.long <- ukb_df_sites_perm %>%
  dplyr::select(sex, age_days, contains("SimSite")) %>%
  pivot_longer(!c(sex, age_days), names_to = "permutation", names_prefix = "SimSite", values_to = "site")

>>>>

```{r}
cn_data <- fread(file="data/lifespan_dataset_dkatlas_CNonly.csv")
#table(cn_data$study)
names(cn_data)
```

@@

```{r}
ukb_df_age.filt <- ukb_df_totals %>%
  dplyr::filter(age_yrs >= 50 & age_yrs <= 80)
#write data
fwrite(ukb_df_age.filt, file="data/ukb_CN_data_agefilt.csv")
```

@@

```{r}
#percent female
r <- table(ukb_df_age.filt$sex)

(r["Female"]/n_unique(ukb_df_age.filt$participant))*100
summary(ukb_df_age.filt$age_yrs)
(table(ukb_df_age.filt$fs_version)["FS6_T1T2"])/(n_unique(ukb_df_age.filt$participant))*100
```

@@

# View the final dataframe
#names(ukb_df_sites_perm)
```

```{r}
sim.perm.long <- ukb_df_sites_perm %>%
  dplyr::select(sex, age_days, contains("SimSite")) %>%
  pivot_longer(!c(sex, age_days), names_to = "permutation", names_prefix = "SimSite", values_to = "site")
